### 2022-04-01 manuscript/thesis.tex
revisions to sections 2 and 3

In the context of an ensemble made from component models submitted from various
sources,
BMA may be preferrable because it does not require that modeling methods for 
individual components be the same. 
In BMA, the final model does not have to be specified
beforehand and the resulting forecast will be a discrete mixture distribution
of all component forecasts. The general form for an ensemble distribution $p^E$
is in \eqref{eq:bma}. Here $p_m$ is the $m^{th}$ component forecast 
distribution and 
$0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling \cite{vrugt2008ensemble},
and minimizing the CRPS of the ensemble
\cite{baran2018combining}.

@@

 \hline
 \end{tabular}
 \begin{minipage}{10cm}
 \caption[Quantile/interval and values storage]{Storage example of quantiles 
 and values of lognormal with $\mu = 1$ and $\sigma = 0.4$}
 \label{table:qstor}
 \end{minipage}
 \end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics[scale=.1]{Images/dens_cum_comp.png}}
\caption[Density/CDF comparison between parametric distribution, sample 
distribution, discretized bin distribution and quantiles]{This figure compares 
the
densities and CDFs of forecast representation types discussed in the left and 
right columns respectively. Each is generated from a lognorma(1,0.4) 
distribution. Blue shows the density and CDF functions. Purple shows a 
histogram and ECDF of 1,000 samples. Red shows bin probabilities and the CDF
function. Green shows quantiles/intervals with corresponding values.}
\label{fig:denscomp}
\end{figure}

\section{Discrete mixture of parametric distributions}
A discrete mixture of parametric distributions forecast representation may be an
attractive alternative to the four types already discussed. A discrete mixture 
would allow for many distribution shapes, a high resolution, storage comparable
to that of discretized bins and quantile representations and the use of the more
common methods for scoring and ensemble building.

A discrete mixture distribution may be constructed in the same way as the
ensemble described in section \ref{section:pardist} in equation 
(\ref{eq:bma}) 
where for $T$ distributions
with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$

@@

Like the standard parametric model, a discrete mixture may be evaluated with
exisiting software (like distr \texttt{R} package \cite{camphausen2007distr}). 
And 
scoring may be done by 
using the LogS, CRPS and IS. The resolution of a discrete mixture is infinite 
and the support need not be limited by submission requirements.

A mixture distribution may be much more flexible than a single component 
parametric distribution in 
terms of distributional shape. According to 
McLachlan and Peel, a finite mixture of 
normal densities with common variance can be used to approximate arbitrarily 
well
any continuous distribution \cite{peel2000finite} (see also 
\cite{nguyen2019approximations}). Thus, for an unconventional probability
distribution -such as MCMC posterior samples- it may be reasonable to 
approximate the distribution by constructing a mixture of normals.
% See section \ref{section:conmix} for an example.

An ensemble model may be built by using (\ref{eq:bma}) only replacing $p_m$
with $p_m^M$ in \ref{eq:dmd}. Solving for weights may also be done similarly, 
though with the 
added complexity of component models being mixture distributions the 
computation is likely to be more expensive. An example where this may be
especially true is when minimizing of CRPS, but the exact mixture doesn't 
result in CRPS in closed form \cite{baran2018combining}. In large projects like
the COVID-19 Forecast Hub, if an equal weight is not assigned to each component,
it may be determined that models not reaching a certain standard of predictive
performance are
assigned an ensemble weight of 0. This would simplify an ensemble model to 
include only the best performing forecasts.

Depending on the number of components a forecaster includes in a mixture 
forecast, the amount of storage per forecast might be as little as for a 
parametric forecast and as much as a forecast hub will allow. In section
\ref{section:conmixforc} we show how a mixture distribution may be constructed,
scored and used to construct an ensemble using software available in 
\texttt{R}.

Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
compares with the other formats discussed in terms of methods for scoring,
information and resolution provided, methods for ensemble building and computer
storage requirement.

\begin{flushleft}
  \begin{table}
    % \begin{adjustwidth}{-3cm}{-1cm}
    \begin{tabular}{ | p{2.4cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
    \hline
    \textbf{Representation} & \textbf{Scoring} & 
    \textbf{Flexibility/Information} & \textbf{Ensemble} &
    \textbf{Storage Requirement}
    \\ \hline \hline

    Parametric & LogS, CRPS, IS & Limited to common distribution families. 
    Infinite resolution
    & BMA & Low 3-6 values per prediction \\ \hline

    Samples & CRPS and IS. LogS after smoothing & Any shape. Resolution may be
    very high but depends on sample size & BMA after smoothing. Resampling 
    otherwise & 
    Hundreds or thousands of values per prediction
    \\ \hline

    Discretized bins & LogS, CRPS, IS &
    Any shape allowed, but limited by binning scheme. Range also may be limited
    & BMA &
    Depends on binning scheme but dozens to hundreds of values
    \\ \hline

@@

    Discrete Mixture & LogS, CRPS, IS. May be more limited by computation & With
    enough component distributions may
    approximate any distribution shape. Infinite resolution& BMA 
    & 3 values to dozens per forecast depending on number of components
    \\ \hline

	 \end{tabular}
	 % \end{adjustwidth}
   \caption[Forecast representation comparison]{This table compares scoring,
   information, ensemble building and storage requirements for the different
   forecast representations discussed.}
   \label{table:repscomp}
   \end{table}

@@

The CDC and the COVID-19 Forecast Hub as well as other collaborative projects
have their own established systems for receiving, 
scoring, and constructing ensemble forecasts. A transition from using bin or 
quantile forecasts to using mixture distribution forecasts
would require
a few adjustments to those systems. In this section we outline how some of these
adjustments may be implemented as well as present some tools which may be used
to score forecasts and construct ensembles from multiple models.

\section{Submission format}
For a collaborative forecast project to run smoothly, model submissions from all 
modelers should follow the same format. For both the CDC flu competition and
the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet with 
columns 
similar to those in tables \ref{table:dbins} and \ref{table:qstor}. Additionally
columns for \texttt{location}, \texttt{target}, \texttt{type}, and \texttt{unit} 
are included.
Here \texttt{location} defines the specific county, state, or country of the 
forecast. The \texttt{target} variable defines what is forecasted for example
season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
the type for the \texttt{value} variable, \texttt{bin} or \texttt{quantile}.
The \texttt{unit} variable defines the time frame of the forecast: week,
two weeks, four weeks, etc. And the \texttt{value} variable is a number that 
either gives probability for a bin or the value for a quantile. Table
\ref{table:dstan} show what a few rows of a forecast 
submission file for the CDC flu competition look like.
For the quantile forecasts of the Forecast Hub, the main changes to Table
\ref{table:dstan} are that the possible values for \texttt{type} 
quantile, and rather than using a \texttt{bin} variable \texttt{quantile} is 
used
with values specified by the Hub. This is seen in Table \ref{table:qstan}

>>>>

In the context of an ensemble made from component models submitted from various
sources,
BMA may be preferable because it does not require that modeling methods for 
individual components be the same. 
In BMA, the final model does not have to be specified
beforehand and the resulting forecast will be a discrete mixture distribution
of all component forecasts. The general form for an ensemble distribution $p^E$
is in \eqref{eq:bma}. Here $p_m$ is the $m^{th}$ component forecast 
distribution and 
$0 \leq w_m \leq 1$ is a weight assigned to that component where $\sum w_m = 1$.
Methods for estimating weights include Maximum Likelihood estimation
\cite{raftery2005using}, MCMC 
sampling \cite{vrugt2008ensemble},
and minimizing the CRPS of the ensemble
\cite{baran2018combining}.

@@

 \hline
 \end{tabular}
 \begin{minipage}{10cm}
 \caption[Quantiles and values storage]{This shows six quantiles
 and values from a lognormal distribution with $\mu = 1$ and $\sigma = 0.4$}
 \label{table:qstor}
 \end{minipage}
 \end{center}
\end{table}

Figure \ref{fig:denscomp} illustrates how the densities and CDFs compare 
between parametric distributions, sample distributions, bin distributions, and
quantiles.

\begin{figure}[htbp]
\begin{center}

\captionsetup{font=scriptsize}
\centerline{\includegraphics[scale=.1]{Images/dens_cum_comp.png}}
\begin{minipage}{10cm}
\caption[Density/CDF comparison between parametric distribution, sample 
distribution, discretized bin distribution and quantiles]{This figure compares 
the
densities and CDFs of forecast representation types discussed in the left and 
right columns respectively. Each is generated from a Lognorma(1,0.4) 
distribution. Blue shows the density and CDF functions. Purple shows a 
histogram and ECDF of 1,000 samples. Red shows bin probabilities and the CDF
function for a bin distribution. Green shows quantiles
with corresponding values.}
\label{fig:denscomp}
\end{minipage}
\end{center}
\end{figure}

\newpage

\section{Mixture distributions}
A discrete mixture of parametric distributions forecast -which we will refer to
as a mixture distribution forecast- representation is an
attractive alternative to the four representations already discussed. 
A mixture distribution forecast
would allow for many distribution shapes, a high resolution, storage comparable
to that of bin and quantile forecasts, and the more common methods for scoring
and ensemble construction may be used.

A mixture distribution may be constructed in the same way as the
ensemble described in section \ref{section:pardist} 
(\ref{eq:bma}) 
where for $T$ distributions
with pdfs $p_t(x)$ and $z_t > 0$ and $\sum_{t=1}^{T} z_t = 1$ we have 
\eqref{eq:dmd}.

@@

Like the parametric, a mixture distribution may be evaluated with
existing software like \texttt{distr} package in \texttt{R} 
\cite{camphausen2007distr}. 
And 
scoring may be done  
using the LogS, CRPS and IS. A mixture distribution, like its parametric 
distribution components, has an infinite resolution.

A mixture distribution may be much more flexible than a single component 
parametric distribution in 
terms of distributional shape. According to 
McLachlan and Peel, a finite mixture of 
normal densities with common variance can be used to approximate arbitrarily 
well
any continuous distribution \cite{peel2000finite} (see also 
\cite{nguyen2019approximations}). Thus, for an unconventional probability
distribution -such as MCMC posterior samples- it may be reasonable to 
approximate the distribution by fitting those samples to a mixture of normal
distributions.
Depending on the number of components a forecaster includes in a mixture 
forecast, the amount of storage per forecast might be as little as for a 
parametric forecast or as permitted in the specific forecast project.

An ensemble model may be built by using \eqref{eq:bma} only replacing $p_m$
with $p_m^M$ in \eqref{eq:dmd}. Solving for weights may also be done by 
maximizing
the likelihood of the forecast or minimizing the CRPS. However with the 
added complexity of component models being mixture distributions the 
computation is likely to be more expensive. An example where this is
true is when trying to minimize the CRPS but the exact mixture doesn't 
produce a closed form CRPS \cite{baran2018combining}. In large projects like
the COVID-19 Forecast Hub, if an equal weight is not assigned to each component,
it may be determined that models not reaching a certain standard of predictive
performance are
assigned an ensemble weight of 0. This would simplify an ensemble model to 
include only the best performing forecasts.

Table \ref{table:repscomp} shows how a discrete mixture distribution forecast 
compares with the other formats discussed in terms of methods for scoring,
information and resolution provided, methods for ensemble building, and computer
storage requirement. To summarize, a continuous mixture distribution has the 
infinite resolution of a parametric distribution with the flexibility of a bin
distribution, a sample distribution, and a set of quantiles. The common proper
scoring rules LogS and CRPS may be used to score it. The storage requirement is
comparable to that of a bin distribution or a set of quantiles. And BMA may be 
used for building an ensemble.
In Section
\ref{section:conmixforc} we show how a mixture distribution may be constructed,
scored and used to construct an ensemble using software available in 
\texttt{R}.

\begin{flushleft}

  \begin{table}
    \begin{center}
    \captionsetup{font=scriptsize}
    \begin{tabular}{ | p{2.4cm} || p{3cm} | p{4cm} | p{3cm} | p{3.5cm} |}
    \hline
    \textbf{Representation} & \textbf{Scoring} & 
    \textbf{Flexibility/Information} & \textbf{Ensemble} &
    \textbf{Storage Requirement}
    \\ \hline \hline

    Parametric distribution & LogS, CRPS, IS & Limited to common 
    distribution families. 
    Infinite resolution
    & BMA & Low 3-6 values per prediction \\ \hline

    Sample distribution & CRPS and IS. LogS after smoothing & Any shape. 
    Resolution may be
    very high but depends on sample size & BMA after smoothing. Resampling 
    otherwise & 
    Hundreds or thousands of values per prediction
    \\ \hline

    Bin distribution & LogS, CRPS, IS &
    Any shape allowed, but limited by binning scheme. Range also may be limited
    & BMA &
    Depends on binning scheme but dozens to hundreds of values
    \\ \hline

@@

    Mixture distribution & LogS, CRPS, IS. May be more limited by computation & 
    With
    enough component distributions may
    approximate any distribution shape. Infinite resolution& BMA 
    & 3 values to dozens per forecast depending on number of components
    \\ \hline

	 \end{tabular}
	 % \end{adjustwidth}
    \begin{minipage}{14cm}
   \caption[Forecast representation comparison]{This table compares scoring,
   information, ensemble building, and storage requirements for the different
   forecast representations discussed. To summarize 
   a continuous mixture distribution has the 
infinite resolution of a parametric distribution with the flexibility of a bin
distribution, a sample distribution, and a set of quantiles. The common proper
scoring rules LogS and CRPS may be used to score it. The storage requirement is
comparable to that of a bin distribution or a set of quantiles. And BMA may be 
used for building an ensemble.}
   \label{table:repscomp}
   \end{minipage}
   \end{center}
   \end{table}

@@

The CDC flu competition and the COVID-19 Forecast Hub as well as other 
collaborative projects
have their own established systems for receiving, 
scoring, and constructing ensemble forecasts. A transition from using bin or 
quantile forecasts to using mixture distribution forecasts
would require
a few adjustments to those systems. In this section we outline how some of these
adjustments may be implemented as well as present some tools which may be used
to build forecasts from submissions, score those forecasts, and construct 
ensembles from them.

\section{Submission format}
For a collaborative forecast project to run smoothly, forecast submissions from 
all forecasters 
should follow the same format. For both the CDC flu competition and
the COVID-19 Forecast Hub, teams provide a \texttt{.csv} spreadsheet which 
contains the distributional information for one or multiple forecasts. Tables
\ref{table:dstan} and \ref{table:qstan} show what variables are included and a
couple rows to illustrate possible values.
The column variables include \texttt{location}, \texttt{target}, \texttt{type},
\texttt{unit}, \texttt{bin} or \texttt{quantile} and \texttt{value}.
Here \texttt{location} defines the specific county, state, or country of the 
forecast. The \texttt{target} variable defines what is forecasted for example
season onset, deaths, hospitalizations, etc. The \texttt{type} variable defines
the type for the \texttt{value} variable, \texttt{bin} or \texttt{quantile}.
The \texttt{unit} variable defines the time frame of the forecast: week,
two weeks, four weeks, etc. And the \texttt{value} variable is a number that 
either gives probability for a bin or the value for a quantile. Table
\ref{table:dstan} show what a few rows of a forecast 
submission file for the CDC flu competition look like.
For the quantile forecasts of the Forecast Hub, the main changes to Table
\ref{table:dstan} are that the possible values for \texttt{type} 
quantile, and rather than using a \texttt{bin} variable \texttt{quantile} is 
used
with values specified by the Hub. This is seen in Table \ref{table:qstan}
